\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using The Same Control Input

### 2018-12-07 journalWallFriction/theory2robAlgs.tex
corrected statement about regular polygons

\subsection{\revision{Convex Workspaces: Accessible Region}}
% worst case analysis
 This algorithm allows two particles to be steered to arbitrary positions as long as the initial particle positions are separated by at least $\epsilon$, and at least one goal position is $\epsilon$ distance from a wall, where $\epsilon$ is a small, positive, user-defined number. 
For a square workspace where the length of each side is $L$, the worst case path length is $(\sqrt{2}+2)L$, and requires at most five moves (see Fig.~\ref{fig:shapeControlMathematica1}f).
\revision{
As the corner angles increase, the number of moves required to access the entire configuration space increases.  
As shown in Fig.~\ref{fig:polygon},  four moves are sufficient for 3-sided polygons, and six moves accesses the entire $\Delta$ configuration space for up to 8-sided polygons.  Eight moves is sufficient for 20-sided polygons, but we have not checked polygons with more sides. For a circular workspace, with corner angles of 180$^\circ$, the worst-case configuration can only be approached asymptotically, as explained in Section~\ref{sec:simulation}.}

>>>>

\subsection{\revision{Convex Workspaces: Accessible Region}}
% worst case analysis
 This algorithm allows two particles to be steered to arbitrary positions as long as the initial particle positions are separated by at least $\epsilon$, and at least one goal position is $\epsilon$ distance from a wall, where $\epsilon$ is a small, positive, user-defined number. 
For a square workspace where the length of each side is $L$, the worst case path length is $(\sqrt{2}+2)L$, and requires at most five moves (see Fig.~\ref{fig:shapeControlMathematica1}f).
\revision{
As the corner angles increase, the number of moves required to access the entire configuration space increases.  
As shown in Fig.~\ref{fig:polygon},  four moves are sufficient for 3-sided regular polygons, and six moves accesses the entire $\Delta$ configuration space for up to 8-sided regular polygons.  Eight moves is sufficient for polygons with less than 14-sides, but we have not checked polygons with more sides. For a circular workspace, with corner angles of 180$^\circ$, the worst-case configuration can only be approached asymptotically, as explained in Section~\ref{sec:simulation}.
If the polygon is irregular, more moves may be required.  The entire configuration space is reachable in four moves for an acute triangle, but obtuse triangles require six moves.
}
